Compositional Equivalences Based on Open pNets

### 2022-10-19 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex

\documentclass[10pt]{article}
\usepackage[latin1]{inputenc} 
\usepackage{alltt,url}
%% Old ttbox definition without frame:
\newenvironment{ttbox}{\begin{alltt}\small\tt}%
                      {\end{alltt}}
\usepackage{color}
\newenvironment{review}{\bgroup\itshape\begin{quote}}{\end{quote}\egroup}

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\thispagestyle{empty}
\addtolength{\textheight}{2cm}
\begin{document}
\section*{Answer to reviewers }
\subsection*{Submission to Journal of Logical and Algebraic Methods in Programming}
\medskip
\begin{ttbox}
Title: Compositional equivalences based on Open pNets
Authors: R. Ameur-Boulifa, L. Henrio, and E. Madelaine
\end{ttbox}
\bigskip
%\subsubsection*{Letter to Reviewers and Editors}
Dear reviewers and editors,

Please find enclosed the revision of our submission to JLAMP. We improved our article according to the comments made by the
anonymous reviewers.

We would first like to thank the reviewers for their analysis of our
paper, and for their insightful comments and advices that extremely strengthen the quality of our paper.
%and the useful advices they gave us.

We detail below the major changes we made in this revision and explain how we addressed them.  \emph{Comments that are  addressed trivially and exactly as suggested by the reviewers are omitted}.

\medskip

%After this, we will review in the next pages the comments of the reviewers and explain how we addressed them.

\section*{Response to reviewer 1}

\begin{review}
blabla de la review
\end{review}
Answer

\begin{review}
suite
\end{review}
bla

\newpage

As explained above, we quote below and reply to text requiring changes that we did not  address in a straightforward manner. We additionally produced a version of the paper highlighting all the changes we made: \TODO{Si tu arrives a produire le latexdiff} \url{url???}

@@

\ERIC{P4, *say that this is like in Symbolic Bisimulation}
\begin{quote}Pas sur du tout, je bosse encore la-dessus...
\end{quote}

\ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?}
\begin{quote} 
\TODO{L'ajout est dans l'introduction pargra. avant la structure}
non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
\end{quote}

\ERIC{P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?}
\begin{quote}
\TODO{L'ajout est dans la section 3.2, fin pargraph 1}
Je n'ai pas redige ca... mais l'idee pourrait etre que en gros oui, et en y ajoutant le formalisme synch vecteurs de Arnold et Nivat, 
mais que notre approache est sensiblement differente, puisque plus syntaxique, pour permettre le developpement de representation finies, d'algorithmes, et d'outils...
\end{quote}

@@

\ERIC{P17, *What is the comoplexity of this "brute force approach"?}
\begin{quote}
le paragraph existant etait difficilement comprehensible et loin de notre implementation dans l'outil. J'ai remplace par quelque chose de plus factuel:
"The definition of this predicate is not constructive. In our tool [39], we construct a logical formula encoding the matching and unification conditions involved, and let an SMT engine (in the current implementation Z3 [30]) decide its satisfiability"
\end{quote}

\ERIC{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies}
\begin{quote}
\TODO{L'ajout est dans la conclusion [30,31]...}

J'ai ajoute 7 ligns ici: "In this platform [...] different encodings of operators".
C'est un peu faible parceque 1) les outils de sont pas encore accessibles en ligne (ca aurait du etre l'achevement du stage de Slava...), et 2) on n'a pas de papier sur un vrai "use-case', a part le AVOCS sur le satellite, mais qui ne fait pas de bisimulation, juste des proprietes temporelles.
\end{quote}

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
correction mineure

\paragraph{A semantics for open pNets based on open automata}
The semantics of pNets can be expressed as a translation to a labelled transition system (LTS), but only if the pNet has no parameter and no hole. Adding parameters to a LTS is quite standard \ERIC{\cite{Lin:96}} but enabling holes inside LTSs is not a standard notion.

@@

\subsection{Composition properties: composition of weak open transitions}
We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton. Like the open automaton, the weak open automaton features valuable composition properties. We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata. These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole. Composition and decomposition properties can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.

>>>>

\paragraph{A semantics for open pNets based on open automata}
The semantics of pNets can be expressed as a translation to a labelled transition system (LTS), but only if the pNet has no parameter and no hole. Adding parameters to a LTS is quite standard \cite{Lin:96} but enabling holes inside LTSs is not a standard notion.

@@

\subsection{Composition properties: composition of weak open transitions}
We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton. Like the open automaton, the weak open automaton features valuable composition properties. We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata. These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole. Composition and decomposition properties can be found as Lemma~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
